---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# idmlr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental) [![License: MIT](https://img.shields.io/badge/License-MIT-yellow.svg)](https://opensource.org/licenses/MIT)
<!-- badges: end -->

The goal of idmlr is to read and (eventually) modify and write InDesign Markup Language (IDML) files.

## Installation

You can install the development version of idmlr from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pkg_install("elipousson/idmlr")
```

## Usage

```{r}
library(idmlr)
```

This is a basic example which shows you how to read an IDML file:

```{r}
idml <- read_idml(system.file("idml/letter_portrait_standard.idml", package = "idmlr"))

idml
```

You can then get the styles from the `idml` object as a list or in a `xml_document` format:

```{r}
get_idml_styles(idml)
```

You can also get fonts and other resources or metadata:

```{r}
get_idml_fonts(idml)
```
